---
title: "Public Synthetic Traceability Demonstration"
format:
  html:
    embed-resources: true
    toc: true
execute:
  echo: false
---

# SYNTHETIC WORKFLOW DEMONSTRATION — NOT A RESEARCH RESULT

This page is software/workflow and structural reproducibility evidence. It is
not a research result, scientific estimate, parity result, protected-data
validation, or evidence that participant-level analyses were reproduced.

```{r}
output_root <- Sys.getenv("TRACE_OUTPUT_ROOT", unset = "")
if (!nzchar(output_root)) stop("TRACE_OUTPUT_ROOT is required")
qc_path <- file.path(output_root, "traceability_qc.csv")
figure_path <- file.path(output_root, "traceability_qc.png")
receipt_path <- file.path(output_root, "traceability_receipt.json")
qc <- utils::read.csv(
  qc_path, stringsAsFactors = FALSE, check.names = FALSE,
  fileEncoding = "UTF-8"
)
receipt <- readLines(receipt_path, warn = FALSE)
receipt_value <- function(field) {
  line <- grep(paste0('"', field, '"'), receipt, value = TRUE, fixed = TRUE)
  sub('.*: "([^"]*)".*', '\\1', line[[1]])
}
```

## Traceability chain

Approved synthetic input → structural QC invocation → machine-readable QC
table → QC figure → this Quarto report → provenance receipt.

- Repository revision: `r receipt_value("repository_revision")`
- Synthetic snapshot: `r receipt_value("synthetic_snapshot_id")`
- Snapshot role: `r receipt_value("synthetic_snapshot_role")`
- Generation status: `r receipt_value("generation_status")`

## Structural QC table

```{r}
knitr::kable(qc, caption = "Synthetic structural and integrity checks")
```

## Structural QC figure

```{r}
#| results: asis
row_y <- seq(80, by = 45, length.out = nrow(qc))
bars <- paste(vapply(seq_len(nrow(qc)), function(index) {
  color <- if (qc$status[[index]] == "PASS") "#2E7D32" else "#B71C1C"
  paste0(
    '<text x="10" y="', row_y[[index]] + 20, '" font-size="14">', qc$check_id[[index]], '</text>',
    '<rect x="230" y="', row_y[[index]], '" width="300" height="30" fill="', color, '" />',
    '<text x="540" y="', row_y[[index]] + 20, '" font-size="14">', qc$status[[index]], '</text>'
  )
}, character(1)), collapse = "")
cat(
  '<svg role="img" aria-label="Synthetic workflow structural QC checklist; every bar represents the PASS or FAIL state of a non-scientific integrity or schema check." ',
  'xmlns="http://www.w3.org/2000/svg" viewBox="0 0 650 340">',
  '<text x="10" y="30" font-size="16" font-weight="bold">SYNTHETIC WORKFLOW DEMONSTRATION — NOT A RESEARCH RESULT</text>',
  bars,
  '</svg>',
  sep = ""
)
```

The displayed values describe only the operation of this public synthetic
workflow. They must not be interpreted as observed cohort findings.
